non_phylo_analyses

### 2018-04-08 reports/non_phylo_model.Rmd
changing habitat traits to yes/no to match rest of traits

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-left_join(traits,response_variables, by="binom") %>%
  filter(SCIENTIFIC_NAME_tree != "not_treated_as_species") %>%
  # drop columns that we aren't inerested in
  select(-brain_size)
```

@@

```{r}
names(df)
df %>%
filter_all(all_vars(!is.na(.)))->df2

naive_mod<-lm(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+log(brain_size)+feeding_habitat_generalism+
     breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+
     movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail")
summary(naive_mod)
dim(df2)
```

>>>>

```{r}
response_variables$binom<-response_variables$SCIENTIFIC_NAME_tree
df<-left_join(traits,response_variables, by="binom") %>%
  filter(SCIENTIFIC_NAME_tree != "not_treated_as_species")
```

@@

```{r}
names(df)
df2 <- df %>%
  # drop columns that we aren't inerested in
  dplyr::select(-brain_size) %>%
filter_all(all_vars(!is.na(.)))

naive_mod<-lm(log(urban_median)~log(mean_body_size)+log(clutch_size)+iucn_status+feeding_habitat_generalism+Habitat_agricultural+Habitat_grass_shrubland+Habitat_tree_forest+breeding_habitat_generalism+granivore+insectivore+carrion_eater+diet_generalism+plant_eater+movement_class+ground_nesting+hollow_nesting+nest_generalism+breeding+nest_aggregation+feeding_aggregation,data=df2,na.action = "na.fail", weights=(df2$N/df2$unique_localities))
summary(naive_mod)
dim(df2)
```
